Supplementary Material

### 2023-11-14 output/paper/manuscript.qmd
Added table LLOQs for steroids. Started kinda intro to paper.

---
title: "Some Title"

metadata-files:
  - ../../../../all_phd/authors.yml

@@

filters:
  - acronyms
  - authors-block
  - ../../../../all_phd/_extensions/wordcount/citeproc.lua
  - ../../../../all_phd/_extensions/wordcount/wordcount.lua

@@

# Abstract {.unnumbered}
**Background**

**Objectives**

**Methods**

**Results**

**Discussion**

@@

- Authorship must follow the ICMJE's criteria. Author names should be listed in ScholarOne and author contributions should be detailed in the cover letter ("Author A..."). Neither names nor contributions should appear in the blinded manuscript. Do not include conflicts of interest.
- The use of the word "effect(s)" as a proxy for "association(s)" is discouraged.
- The length of the abstract must be less or equal than 200 words, and should be unstructured, stating the research questions, the methods used, and the results and conclusions of the research.
- The length must be <4,000 words, excluding abstract, references, tables, figure captions, acknowledgments, and Supplementary Material.
  - Use the AMA format.
  - In-text citations: full-sized Arabic numerals in parentheses within the sentence.
- Submission: SER members receive a 10% discount on the fees per page. This should be requested in the cover letter. Also 20% discount for Open Access charges. If uploading a single file (document, tables, figures, SM), designate the file as "Main document - anonymous".

# Introduction {#sec-intro}

**Do not use "Introduction" as a heading**.

>>>>

---
title: "Estimating associations between childhood exposure to non-persistent endocrine disruptors, corticosteroids, and neurodevelopment: A study based on the parametric g-formula"

# metadata-files:
#   - ../../../../all_phd/authors.yml

@@

filters:
  - acronyms
  # - authors-block
  - ../../../../all_phd/_extensions/wordcount/citeproc.lua
  - ../../../../all_phd/_extensions/wordcount/wordcount.lua

@@

# Abstract {.unnumbered}

@@

- Authorship must follow the ICMJE's criteria. Author names should be listed in ScholarOne and author contributions should be detailed in the cover letter ("Author A..."). Neither names nor contributions should appear in the blinded manuscript. Do not include conflicts of interest.
- The use of the word "effect(s)" as a proxy for "association(s)" is discouraged.
- The length of the abstract must be less or equal than 200 words, and should be unstructured, stating the research questions, the methods used, and the results and conclusions of the research.
- The length must be <4,000 words, excluding abstract, references, tables, figure captions, acknowledgments, and Supplementary Material.
  - In-text citations: full-sized Arabic numerals in parentheses within the sentence.
- Submission: SER members receive a 10% discount on the fees per page. This should be requested in the cover letter. Also 20% discount for Open Access charges. If uploading a single file (document, tables, figures, SM), designate the file as "Main document - anonymous".

### 2023-11-14 output/paper/sections/introduction.qmd
Added table LLOQs for steroids. Started kinda intro to paper.

## Background and rationale {#sec-background}

- Brief review of the literature to summarize current knowledge.
  - Acknowledge inconsistencies.
  - For each study, indicate whether it was observational or experimental, and note key characteristics of study populations or experimental models.
- Explain the scientific background and rationale for the investigation being reported.
  - Identify knowledge gaps addressed by the current study.
- Provide context for the study: include information on exposures and outcomes, and why they are relevant to environmental health.

## Objectives {#sec-objectives}

- Provide a clear description of the study hypotheses/aims/objectives, and eventually an overview of the approach used to address them.

>>>>

In the present study, we estimated associations between 1) non-persistent \acr{edcs} and attention, 2) non-persistent \acr{edcs} and corticosteroids, and 3) corticosteroids and attention, using the parametric g-formula and average contrasts, in children of a large prospective birth cohort in Europe.

### 2023-11-14 output/paper/si.qmd
Added table LLOQs for steroids. Started kinda intro to paper.

>>>>

```{r lloq-mets}
#| label: tbl-lloq-mets
#| tbl-cap: Lower limits of quantification for the corticosteroids

lloq_mets <- load_steroids()$loq |>
  tidylog::mutate(
    metabolite = stringr::str_replace(
      metabolite,
      "^X", ""
    )
  ) |>
  tidylog::rename(
    lloq = "loq"
  )
gt::gt(lloq_mets |> dplyr::arrange(metabolite)) |>
  gt::tab_footnote(
    footnote = "Lower limit of quantification expressed in nanograms per millilitre.",
    locations = gt::cells_column_labels(
      columns = lloq
    )
  )
```
